Exploring dimensions of biodiversity in Japanese ferns

### 2020-09-18 ms/SI.Rmd
Render ms word

---
title: "Exploring dimensions of biodiversity in Japanese ferns"
bibliography: "main_library.bib"
mainfont: Roboto-Regular.ttf
fontsize: 11pt
mainfontoptions: 
- BoldFont=Roboto-Bold.ttf
- ItalicFont=Roboto-Italic.ttf
- BoldItalicFont=Roboto-BoldItalic.ttf
output: 
  bookdown::pdf_document2:
    citation_package: none # Use pandoc default, otherwise csl can't be used for reference formatting
    toc: no
    number_sections: no
    fig_caption: yes
    keep_tex: no
    latex_engine: xelatex
    pandoc_args: [ "--csl", "journal-of-biogeography.csl"]
    includes:
      in_header: newphyt.sty
header-includes: 
  \usepackage{float}
  \makeatletter\renewcommand*{\fps@figure}{H}\makeatother
editor_options: 
  chunk_output_type: console
# nocite: | 
---

>>>>

---
title: "Exploring dimensions of biodiversity in Japanese ferns"
bibliography: "main_library.bib"
mainfont: Roboto-Regular.ttf
fontsize: 11pt
mainfontoptions: 
- BoldFont=Roboto-Bold.ttf
- ItalicFont=Roboto-Italic.ttf
- BoldItalicFont=Roboto-BoldItalic.ttf
output: 
  bookdown::pdf_document2:
    citation_package: none # Use pandoc default, otherwise csl can't be used for reference formatting
    toc: no
    number_sections: no
    fig_caption: yes
    keep_tex: yes
    latex_engine: xelatex
    pandoc_args: [ "--csl", "journal-of-biogeography.csl"]
    includes:
      in_header: newphyt.sty
header-includes: 
  \usepackage{float}
  \makeatletter\renewcommand*{\fps@figure}{H}\makeatother
editor_options: 
  chunk_output_type: console
# nocite: | 
---
